Associahedra for finite type cluster algebras \\ and minimal relations between $\b{g}$-vectors

### 2023-02-21 thirdPaper/draft/typeConeAssociahedra.tex
minor changes

\pagebreak
We now focus on the normal fan of~$\Asso[n]$.
Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, its normal fan has a one-dimensional lineality (spanned by the all-ones vector).
To factor out the lineality, let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and ${\pi : \R^{n+1} \to \HH}$ denote the orthogonal projection.
We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$. Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan consisting of the projections under~$\pi$ of the normal cones of $\Asso[n]$. With the choice of a basis, we can identify $\HH$ with $\R^n$ and depict~$\Asso[n]$ as a full-dimensional polytope with normal fan~$\gvectorFan[n]$.

@@

We first show that~$\mu$ and~$\nu$ are compatible.
Let~$\tau$ be a maximal common substring of~$\mu$ and~$\nu$.
If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ and $\mu$ and~$\nu$ are not kissing at~$\tau$.
We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
We distinguish two different cases:
\begin{itemize}
\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ forms a cycle in~$\quiver$. If~$\tau$ is reduced to a vertex, then we have a $2$-cycle. Otherwise, since~$\alpha\tau$ is a substring of~$\nu$ and~$\alpha'\tau$ is a substring of~$\nu$, the cycle~$\alpha \tau \alpha'$ contains a unique relation~$\alpha'\alpha$. This rules out this case under the assumption that~$\quiver$ is brick and $2$-acyclic. The case when~$\tau$ appears after~$\sigma$ in both~$\mu$ and~$\nu$ is symmetric.
\item If~$\tau$ appears before~$\sigma$ in~$\mu$ and after~$\sigma$ in~$\nu$, then~$\omega$, $\mu$ and~$\nu$ finish at the same blossom so that~$\mu$ and~$\nu$ are not kissing at~$\tau$. The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is symmetric.
\end{itemize}
We conclude that~$\mu$ and~$\nu$ are non-kissing, which also implies that~$\{\mu, \nu, \omega\}$ and~$\{\mu, \nu, \omega'\}$ are non-kissing faces of~$\NKC$.
We can therefore consider a non-kissing facet~$F$ containing~$\{\mu, \nu, \omega\}$.

>>>>

\pagebreak
We now focus on the normal fan of~$\Asso[n]$.
Since~$\Asso[n]$ lives in a hyperplane of~$\R^{n+1}$, its normal fan has a one-dimensional lineality (spanned by the all-ones vector).
To factor out the lineality, let~$\HH \eqdef \bigset{\b{x} \in \R^{n+1}}{\sum_{\ell \in [n+1]} \b{x}_\ell = 0}$ and ${\pi : \R^{n+1} \to \HH}$ denote the orthogonal projection.
We denote by~$\gvectorFan[n]$ the intersection of the normal fan of~$\Asso[n]$ with~$\HH$. 
Note that~$\gvectorFan[n]$ is an $n$-dimensional essential complete simplicial fan in~$\HH$, which is actually the normal fan of~$\pi(Asso[n])$ in~$\HH$. 
With the choice of a basis, we can identify $\HH$ with $\R^n$ and depict~$\gvectorFan[n]$ and~$\pi(\Asso[n])$ in~$\R^n$.

@@

We first show that~$\mu$ and~$\nu$ are compatible.
Let~$\tau$ be a maximal common substring of~$\mu$ and~$\nu$.
If~$\sigma$ and~$\tau$ are not disjoint, then~$\sigma = \tau$ (as $\tau \subseteq \sigma$ and~$\mu$ and~$\nu$ differ at the extremities of~$\sigma$) and $\mu$ and~$\nu$ are not kissing at~$\tau$.
We can therefore assume that $\tau$ appears completely before or completely after~$\sigma$ in both~$\mu$ and~$\nu$.
We distinguish two different cases:
\begin{itemize}
\item If~$\tau$ appears before~$\sigma$ in both~$\mu$ and~$\nu$, then~$\alpha \tau \alpha'$ forms a cycle in~$\quiver$. If~$\tau$ is reduced to a vertex, then we have a $2$-cycle. Otherwise, since~$\alpha\tau$ is a substring of~$\nu$ and~$\alpha'\tau$ is a substring of~$\nu$, the cycle~$\alpha \tau \alpha'$ contains a unique relation~$\alpha'\alpha$. This rules out this case under the assumption that~$\quiver$ is brick and $2$-acyclic. The case when~$\tau$ appears after~$\sigma$ in both~$\mu$ and~$\nu$ is symmetric.
\item If~$\tau$ appears before~$\sigma$ in~$\mu$ and after~$\sigma$ in~$\nu$, then~$\omega$, $\mu$ and~$\nu$ finish at the same blossom so that~$\mu$ and~$\nu$ are not kissing at~$\tau$. The case when~$\tau$ appears after~$\sigma$ in~$\mu$ and before~$\sigma$ in~$\nu$ is symmetric.
\end{itemize}
We conclude that~$\mu$ and~$\nu$ are non-kissing, which also implies that~$\{\mu, \nu, \omega\}$ and~$\{\mu, \nu, \omega'\}$ are non-kissing faces of~$\NKC$.
We can therefore consider a non-kissing facet~$F$ containing~$\{\mu, \nu, \omega\}$.
